The sparseHessianFD package

### 2015-05-04 README.Rmd
done for the night

The `sparseHessian.new` function returns an object of class
sparseHessianFD.  This class contains methods to return the function
value, gradient and Hessian.  The Hessian is returned in a sparse,
compressed format as a `dgCMatrix` object (defined in the *Matrix*
package).

@@

```{r, eval=FALSE}
P <- rnorm(N) ## random "starting value" for initialization
obj <- sparseHessianFD.new(P, f, df, rows, cols)
X <- rnorm(N) ## another set of variables at which the function is evaluated
val <- obj$fn(X) ## function value
gr <- obj$gr(X) ## gradient
hess <- obj$hessian(X)  ## Hessian, as a sparse dgCMatrix object
```

>>>>

The `sparseHessianFD` function returns an object of class
sparseHessianFD.  This class contains methods to return the function
value, gradient and Hessian.  The Hessian is returned in a sparse,
compressed format as a `dgCMatrix` object (defined in the *Matrix*
package).

@@

```{r, eval=FALSE}
P <- rnorm(N) ## random "starting value" for initialization
obj <- sparseHessianFD(P, f, df, rows, cols)
X <- rnorm(N) ## another set of variables at which the function is evaluated
val <- obj$fn(X) ## function value
gr <- obj$gr(X) ## gradient
hess <- obj$hessian(X)  ## Hessian, as a sparse dgCMatrix object
```
